The brightness and spatial distributions of terrestrial radio sources

### 2013-01-17 articles/Article-RFI-distribution/article-rfi-distribution.tex
Slight rewording

We assume that the stochastic nature of $I$, that is caused by the spread of transmitters with different intrinsic strengths, also has little effect on the $\log N$ -- $\log S$ histograms. Nevertheless, it is unlikely that $I$ follows a uniform or Gaussian distribution, because the distribution will contain few strong transmitters (such as radio stations) and many weak transmitters (such as remote controls). Therefore, variable $I$ might follow a power law by itself. It is likely that strong transmitters transmit more on average, and therefore contaminate more samples as well. High-power transmitters, such as radio stations, have a typical transmitting power in the order of 100 kW. Low-power transmitters, such as remote controls, transmit with an order of 100 mW. Therefore, these devices have a spread of around 6 orders of magnitudes in power. As long as the exponent of the power law of $I$ is less steep (i.e., less negative) compared to the power law caused by the spatial distribution, the spatial distribution will dominate the histogram at high amplitudes. With a spatial $-1.5$ power law and the given transmitting powers, the low-power transmitters should contaminate a factor of $10^9$ more samples compared to the high-power transmitters to dominate the high-amplitude distribution, which is unlikely. Therefore, it is likely that the spatial distribution will dominate the power law in the histogram.

>>>>

We assume that the stochastic nature of $I$, that is caused by the spread of transmitters with different intrinsic strengths, also has little effect on the $\log N$ -- $\log S$ histograms. Nevertheless, it is unlikely that $I$ follows a uniform or Gaussian distribution, because the distribution will contain few strong transmitters (such as radio stations) and many weak transmitters (such as remote controls). Therefore, variable $I$ might follow a power-law distribution by itself. It is likely that strong transmitters transmit more on average, and therefore contaminate more samples as well. High-power transmitters, such as radio stations, have a typical transmitting power in the order of 100 kW. Low-power transmitters, such as remote controls, transmit with an order of 100 mW or even less. Therefore, these devices have a spread of around 6 orders of magnitudes in power. As long as the exponent of the power law of $I$ is less steep (i.e., less negative) compared to the power law caused by the spatial distribution, the spatial distribution will dominate the histogram at high amplitudes. With a spatial $-1.5$ power law and the given transmitting powers, the low-power transmitters should contaminate a factor of $10^9$ more samples compared to the high-power transmitters to dominate the high-amplitude distribution, which is unlikely. Therefore, it is likely that the spatial distribution will dominate the power law in the histogram.
